Consumption and resistance across states

### 2017-02-22 states/resistance/report2/state-report.Rmd
new summaries

gram_negs = c('Escherichia coli', 'Klebsiella pneumoniae', 'Proteus mirabilis',
              'Enterobacter cloacae', 'Klebisella oxytoca')
gram_poss = c('Coagulase-negative staphylococci', 'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)', 'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

# State-level consumption data
state_consumption = read_tsv('../../bene-consumption/state-consumption-2011.tsv') %>%
  rename(consumption_drug=drug) %>%
  select(state, consumption_drug, claims_per_1k_ppl, did)

>>>>

gram_negs = c('Escherichia coli', 'Klebsiella pneumoniae',
              'Proteus mirabilis', 'Enterobacter cloacae',
              'Klebisella oxytoca', 'Enterococcus faecium')
gram_poss = c('Coagulase-negative staphylococci',
              'Methicillin-resistant S. aureus (MRSA)',
              'Methicillin-susceptible S. aureus (MSSA)',
              'Streptococcus pneumoniae (non-meningitis)',
              'Staphylococcus aureus')
organisms = c(gram_negs, gram_poss)

@@

# State-level consumption data
state_consumption = read_tsv('../../bene-consumption/state_usage_2011.tsv') %>%
  rename(consumption_drug=antibiotic) %>%
  select(state, consumption_drug, claims_per_1k_ppl, did)
